Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-03 be.tex
appendix

Integrating both sides of equation~\eqref{eq:enCons} from the stagnation radius $r = \rs$ outwards,
\begin{align}
  r^2 \rho v \left(\ke+\Phi+\gammaf \frac{p}{\rho} \right)= \int_{\rs}^{r}
    r^2 \left(q \kew + q\Phi\right) dr
    \label{eq:enConsInt}
\end{align}
From mass continuity (eq.~[\ref{eq:drhodt}]) the mass flux can be written
\be
 f\equiv r^2 \rho v = q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right],
 \label{eq:massFlux}
\ee
where $x \equiv r/\rs$ and we have used the fact that the mass source term $q = q_o x^{-\delta}$ is proportional to the stellar density.  Likewise, the gravitational potential $\Phi$ is given by
\begin{align}
\Phi \simeq -\frac{G \Menc}{r} -4 \pi G \int_{r}^{\rb} \rhostar(r') r' dr',
\label{eq:Phi}
\end{align}
where by truncating the integral at $r = \rb$ we are neglecting the contribution to the potential of the stars outside of the break radius.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$. If $\zeta<\zeta_c$ outflows are
  only possible if the ratio of the stagnation radius to the influence
  radius exceeds a minimum value. Plotted as a function of the ratio
  of the break radius to the influence radius ($\rb/\rsoi$) {\emph Bottom
    Panel:} Mininmum value for ratio of the stagnation radius to the
  influence radius, $\rs/\rsoi$ for core galaxies ($\Gamma=0.1$)
  derived by requiring enthalpy of the gas to remain positive out to
  the break radius $\rb$. This is calculated numerically from
  equation~\eqref{eq:enthAnal}. The x-intercept of each curve
  corresponds to the critical $\zeta_c$}
\end{figure}

>>>>

Integrating both sides of equation~\eqref{eq:enCons} from the
stagnation radius $r = \rs$ outwards,
\begin{align}
  r^2 \rho v \left(\ke+\Phi+\gammaf \frac{p}{\rho} \right)= \int_{\rs}^{r}
    r^2 \left(q \kew + q\Phi\right) dr
    \label{eq:enConsInt}
\end{align}
From mass continuity (eq.~[\ref{eq:drhodt}]) the mass flux can be
written

\begin{equation}
 f\equiv r^2 \rho v = q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right],
 \label{eq:massFlux}
 \end{equation}

where $x \equiv r/\rs$ and we have used the fact that the mass
 source term $q = q_o x^{-\delta}$ is proportional to the stellar
 density.  Likewise, the gravitational potential $\Phi$ is given by
\begin{align}
\Phi \simeq -\frac{G \Menc}{r} -4 \pi G \int_{r}^{\rb} \rhostar(r') r' dr',
\label{eq:Phi}
\end{align}
where by truncating the integral at $r = \rb$ we are neglecting the
contribution to the potential of the stars outside of the break
radius.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$ for core ($\Gamma=0.1$)
  galaxies. If $\zeta<\zeta_c$ outflows are only possible if the ratio
  of the stagnation radius to the influence radius exceeds a minimum
  value. Plotted as a function of the ratio of the break radius to the
  influence radius ($\rb/\rsoi$) {\emph Bottom Panel:} Mininmum value
  for ratio of the stagnation radius to the break radius, $\rs/\rb$
  for core galaxies ($\Gamma=0.1$) derived by requiring the Bernoulli
  parameter of the gas to remain positive out to the break radius
  $\rb$. This is calculated numerically from
  equation~\eqref{eq:enthAnal}.}
\end{figure}
